Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-23 ms/main.tex
fig 1 caption by OLE

\section*{Figures}
%%% Figure: model illustration
\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
  \caption{\textbf{Cultural horizontal transmission with assortment.} Transmission occurs between interacting partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$, where $\alpha$ is the \emph{interaction-transmission association} parameter.
  }
  \label{fig:illustration}
\end{figure}

>>>>

\section*{Figures}
%%% Figure: model illustration
\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\textwidth]{Illustration.pdf}
  \caption{\textbf{Model illustration.} 
  \textbf{(a)} Prisoners' dilemma payoff matrix, showing The fitness of phenotype $\phi_1$ when interacting with phenotype $\phi_2$.
  \textbf{(b)} Individuals socially interact in pairs in a prisoners' dilemma game. Horizontal cultural transmission occurs with a random individual from the population, with probability $1-\alpha$, or with the social partner, with probability $\alpha$, where $\alpha$ is the interaction-transmission association parameter.
  \textbf{(c)} The probability of successful horizontal  cultural transmission of phenotypes $A$ and $B$ is $T_A$ and $T_B$ respectively.
  \textbf{(d)} Offspring inherit their parent phenotype with probability $v$, or the phenotype of a random non-parental adult with probability $1-v$.
    }
  \label{fig:illustration}
\end{figure}
